Title Goes Here

### 2021-04-13 analysis/paper/shceof.Rmd
Agrega círculos de latitud
Closes #29

grid <- theme(panel.grid = element_line(color = "gray10", size = 0.4, linetype = 3))
no_grid <- theme(panel.grid = element_blank())

@@

  geom_qmap(~.x[lat <= -20], size = 0.1) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom(10))  +
  scale_y_latitude() +
  scale_x_longitude() +
  coord_polar() +
  theme(axis.text = element_blank()) +
  facet_wrap(.~cEOF, ncol = 2, labeller = labeller(lev = lab_lev))  +
  tagger::tag_facets("rc")  +
  theme(panel.spacing = grid::unit(-.7, "lines"))
```

@@

  geom_qmap(~ .x[lat <= -20]) +
  scale_x_longitude() +
  scale_y_latitude() +
  scale_linetype_manual(values = c("1" = 1, "-1" = 2), labels = c("1" = "+", "-1" = "-"),
                        guide = "none") +
  facet_grid( lev  ~  cEOF,
             labeller = labeller(lev = lab_lev,
                                 cEOF = var)) +
  coord_quickmap(ylim = c(NA, -20)) +
  theme(legend.title = element_blank()) +
  coord_polar() +
  axis_labs_smol +
  tag_facets(tag = "cr")

@@

    scale_x_longitude() +
    scale_y_latitude() +
    facet +
    coord_polar() +
    axis_labs_smol +
    tag_facets("rc")
}
```

@@

  geom_contour_pval(aes(z = p.value)) +
  geom_hline(yintercept = o3wave_lats, size = 0.3, alpha = 0.5) +
  geom_qmap(~.x[lat <= -20]) +
  scale_fill_divergent_discretised("Total Ozone Column", 
                                   guide = guide_colorsteps_bottom(15)) + 
  scale_x_longitude() +
  scale_y_latitude() +
  scale_linetype(guide = "none") +
  coord_polar() +

@@

```{r eof-filtered, fig.cap = "Spatial pattern of the leading EOF of 200 hPa geopotential height with the variability of cEOF2 filtered out South of 20º. Arbitrary units.", fig.width=2.5, fig.height=2.5}
eof_filtered <- era5 %>% 
  .[sep_ReIm(cEOF2, format = "wide")[, hgt := NULL], on = .NATURAL] %>% 
  .[lev == 200] %>% 
  .[lat <= -20] %>% 
  .[season(time) == "SON"] %>% 
  .[, hgt := resid(.lm.fit(cbind(1, Real, Imaginary), hgt)), .(lon, lat, lev, season(time))] %>%
  .[, eof := Anomaly(hgt)*sqrt(cos(lat*pi/180)), by = .(lon, lat, lev, season(time))] %>% 
  EOF(eof ~ lon + lat | time, n = 1, data = .)

@@

  geom_contour_tanaka(aes(z = eof), global.breaks = TRUE, 
                      breaks = AnchorBreaks(0,0.5,  exclude = 0)) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom()) +
  geom_qmap(~.x[lat <= -20]) +
  scale_x_longitude() +
  scale_y_latitude() +
  coord_polar() +
  facet_wrap(~EOF, ncol = 3, labeller = labeller(EOF = var)) +
  axis_labs_smol +
  theme(axis.text = element_blank()) +
  tag_facets("rc")
```

>>>>

grid <- theme(panel.grid = element_line(color = "gray10", size = 0.4, linetype = 3))
no_grid <- theme(panel.grid = element_blank())
grid_y <- theme(panel.grid.major.y = element_line(color = "gray60", size = 0.1))

@@

  geom_qmap(~.x[lat <= -20], size = 0.1) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom(10))  +
  scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  scale_x_longitude() +
  coord_polar() +
  theme(axis.text = element_blank()) +
  facet_wrap(.~cEOF, ncol = 2, labeller = labeller(lev = lab_lev))  +
  tagger::tag_facets("rc")  +
  theme(panel.spacing = grid::unit(-.7, "lines")) +
  grid_y
```

@@

  geom_qmap(~ .x[lat <= -20]) +
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  scale_linetype_manual(values = c("1" = 1, "-1" = 2), labels = c("1" = "+", "-1" = "-"),
                        guide = "none") +
  facet_grid( lev  ~  cEOF,
             labeller = labeller(lev = lab_lev,
                                 cEOF = var)) +
  coord_quickmap(ylim = c(NA, -20)) +
  theme(legend.title = element_blank()) +
  coord_polar() +
  axis_labs_smol +
  tag_facets(tag = "cr") +
  grid_y
```

@@

    scale_x_longitude() +
      scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
    grid_y +
    facet +
    coord_polar() +
    axis_labs_smol +
    tag_facets("rc")
}
```

@@

  geom_contour_pval(aes(z = p.value)) +
  geom_hline(yintercept = o3wave_lats, size = 0.3, alpha = 0.8) +
  geom_qmap(~.x[lat <= -20]) +
  scale_fill_divergent_discretised("Total Ozone Column", 
                                   guide = guide_colorsteps_bottom(15)) + 
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  grid_y +
  scale_linetype(guide = "none") +
  coord_polar() +

@@

```{r eof-filtered, fig.cap = "Spatial pattern of the leading EOF of 200 hPa geopotential height with the variability of cEOF2 filtered out South of 20º. Arbitrary units.", fig.width=2.5, fig.height=2.5}
cEOF2 <- ceof$eof[[1]]$left[cEOF == "cEOF2"] %>% 
  copy() %>% 
  .[, cEOF := NULL] %>% 
  .[]

eof_filtered <- era5 %>% 
  .[sep_ReIm(cEOF2, format = "wide")[, hgt := NULL], on = .NATURAL] %>% 
  .[lev == 200] %>% 
  .[lat <= -20] %>% 
  .[season(time) == "SON"] %>% 
  .[, hgt := resid(.lm.fit(cbind(1, Real, Imaginary), hgt)), .(lon, lat, lev, season(time))] %>%
  .[, eof := Anomaly(hgt)*sqrt(cos(lat*pi/180)), by = .(lon, lat, lev, season(time))] %>% 
  EOF(eof ~ lon + lat | time, n = 1, data = .)

@@

  geom_contour_tanaka(aes(z = eof), global.breaks = TRUE, 
                      breaks = AnchorBreaks(0,0.5,  exclude = 0)) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom()) +
  geom_qmap(~.x[lat <= -20]) +
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  grid_y +
  coord_polar() +
  facet_wrap(~EOF, ncol = 3, labeller = labeller(EOF = var)) +
  axis_labs_smol +
  theme(axis.text = element_blank()) +
  tag_facets("rc")
```
